NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2018-03-23 Manuscript/manuscriptPS.tex
Add results delivered by R. Nencini and conclusion that currect CHARMM-GUI parameters give too weak Ca2+ binding to the manuscript

The headgroup order parameter changes of POPC and POPS from POPC:POPS (5:1) bilayers
as a function of Ca$2+$ concentration from different
simulations and experiments \cite{roux90} are shown in Fig. \ref{changesWITHCaClPS}.
The results suggest that Ca2+ ions clearly overbind in simulations with
MacRog model, as expected from previous results for PC lipid bilayers \cite{catte16}.
It should be noted, however, that the lowest concentration (100mM) gives
a good agreemet with experiments \todo{Should be analyze/discuss this further?}.
Surprisingly, the calcium binding seems to be too weak CHARMM36 simulations
\todo{This is most likely due to the new interactions added to CHARMM-GUI:
  http://nmrlipids.blogspot.com/2017/12/nmrlipids-iv-current-status-and.html?showComment=1519913688317\#c5312059274016196300
}.
The density profiles of Ca2+ from the simulations are shown in Fig. \ref{CAdensPCPSmixture}.
\todo{More simulation data for systems with PS lipids and CaCl$_2$ would be probably useful}

@@

>>>>

The headgroup order parameter changes of POPC and POPS from POPC:POPS (5:1) bilayers
as a function of Ca$2+$ concentration from different
simulations and experiments \cite{roux90} are shown in Fig. \ref{changesWITHCaClPS}.
The results suggest that Ca2+ ions clearly overbind in simulations with
MacRog model, as expected from previous results for PC lipid bilayers \cite{catte16}.
It should be noted, however, that the lowest concentration (100mM) gives
a good agreemet with experiments \todo{Should be analyze/discuss this further?}.
Surprisingly, the calcium binding seems to be too weak CHARMM36 simulations.
This is due to the NBfix interaction parameters from Ref. \citenum{kim16}, which are incorporated
to CHARMM-GUI. These parameters give also too weak binding of calcium to pure POPC bilayer,
as shown in Figs. \ref{OP_CHARMM_CaCl_POPC_NBFix} and \ref{density_profile_CHARMM_CaCl_POPC_NBFix}.
The density profiles of Ca2+ from the simulations are shown in Fig. \ref{CAdensPCPSmixture}.
\todo{More simulation data for systems with PS lipids and CaCl$_2$ would be probably useful}

@@

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/OP_CHARMM_CaCl_POPC_NBFix.pdf}
  \caption{\label{OP_CHARMM_CaCl_POPC_NBFix}
  The response of headgroup order parameters to the fixed amount of cationic surfactants in
  POPC bilayer is compared between simulations and experiments \cite{scherer89}.}
\end{figure}

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/density_profile_CHARMM_CaCl_POPC_NBFix.pdf}
  \caption{\label{density_profile_CHARMM_CaCl_POPC_NBFix}
  The response of headgroup order parameters to the fixed amount of cationic surfactants in
  POPC bilayer is compared between simulations and experiments \cite{scherer89}.}
\end{figure}
